---
output:
  word_document:
    reference_docx: "../inst/report_templates/slim_template.docx"
params:
   mv: NULL
   studentids: NULL
   grade: NULL
   growth_percentile_target: 80
   measurementscale: 'Reading'
   baseline: 'Spring 2015-2016'
   endpoint: 'Spring 2016-2017'
   linking_chart: NULL
   linking_data: NULL
---

---
title: `r paste(params$measurementscale, 'MAP Class Growth Goals')`
---

```{r setup, echo=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  error = FALSE,
  dpi = 300
)
```

```{r libraries}

library(gridExtra)

```

```{r data1}

baseline_cdf <- mapvizieR::mv_limit_cdf(
  mapvizieR_obj = params$mv,
  studentids = params$studentids,
  measurementscale = params$measurementscale
) %>%
dplyr::filter(
  termname == params$baseline
)

#hacky holdover hotfixes
constant_grade <- baseline_cdf$grade %>% table() %>% sort(TRUE) %>% names() %>% extract(1) %>% as.numeric()
baseline_cdf$grade <- constant_grade

baseline_cdf <- baseline_cdf %>% 
  dplyr::group_by(
    measurementscale, map_year_academic, 
    fallwinterspring, termname, grade
  )

baseline_rit <- mean(baseline_cdf$testritscore, na.rm = TRUE) 
baseline_sum <- mapvizieR::summary.mapvizieR_cdf(baseline_cdf)

num_students <- length(params$studentids %>% unique())
valid_mask <- params$studentids %in% baseline_cdf[!is.na(baseline_cdf$testritscore), ]$studentid
missing_ids <- params$studentids[!valid_mask] %>% unique()
num_missing <- length(missing_ids)
missing_logical <- num_missing > 0
nys_logical <- params$grade >= 3
```

```{r cgp1}

start_season <- gsub(" .*$", "", params$baseline)
end_season <- gsub(" .*$", "", params$endpoint)

cgp_slim <- calc_cgp(
  measurementscale = params$measurementscale,
  end_grade = params$grade,
  growth_window = paste0(start_season, ' to ', end_season),
  baseline_avg_rit = baseline_sum$mean_testritscore,
  calc_for = c(1, 5, 20, 50, 80, 95, 99)
)

```

```{r cgp2}

cgp_targets <- cgp_slim$targets

goal_growth <- cgp_targets[cgp_targets$cgp == params$growth_percentile_target, ]$growth_target
goal_endpoint_rit <- baseline_rit + goal_growth
goal_halfway_rit <- baseline_rit + (goal_growth / 2)

goal_endpoint_cohort_status_npr <- cohort_mean_rit_to_npr(
  params$measurementscale, 
  params$grade, 
  end_season,
  goal_endpoint_rit
)
```


```{r plots1}

p_cgp_targets <- cgp_target_spread_plot(
  cgp_prep = cgp_slim
)

```

```{r plots2}
#shitty holdover logic
temp_mv <- params$mv

if (start_season == 'Spring') {
  temp_mv$cdf <- temp_mv$cdf %>%
    dplyr::filter(
      grade_level_season <= params$grade - 1
    )
}

#make plots
rit_trace_simple <- cohort_rit_trace_plot(
  mapvizieR_obj = temp_mv,
  studentids = params$studentids,
  measurementscale = params$measurementscale,
  match_method = 'no matching',
  first_and_spring_only = FALSE,
  entry_grade_seasons = c(-99),
  collapse_schools = TRUE,
  retention_strategy = 'collapse',
  small_n_cutoff = -1
)

status_trace_rit <- cohort_status_trace_plot(
  mapvizieR_obj = temp_mv,
  studentids = params$studentids,
  measurementscale = params$measurementscale,
  match_method = 'no matching',
  first_and_spring_only = TRUE,
  entry_grade_seasons = c(-99),
  collapse_schools = TRUE,
  retention_strategy = 'collapse',
  small_n_cutoff = -1,
  plot_labels = 'RIT'
)

status_trace_npr <- cohort_status_trace_plot(
  mapvizieR_obj = temp_mv,
  studentids = params$studentids,
  measurementscale = params$measurementscale,
  match_method = 'no matching',
  first_and_spring_only = TRUE,
  entry_grade_seasons = c(-99),
  collapse_schools = TRUE,
  retention_strategy = 'collapse',
  small_n_cutoff = -1,
  plot_labels = 'NPR'
)

```


# About these students

There are `r num_students` students in this group.  **`r length(missing_ids)`** of them do not yet have a baseline MAP score.

```{r child1, eval=missing_logical, child = 'missing_stu.Rmd'}

```


# `r params$measurementscale` Prior Achievement

Here is the historical class average RIT for these students.  (This plot shows all historical data for all `r num_students` students - it is _not_ limited to continuously enrolled students.  It does, however, exclude students who have transferred out of the school and are no longer part of the presently enrolled `r num_students`-student group.)

```{r rit_trace, fig.width = 8, fig.height = 4}

rit_trace_simple

```

The background reference lines on the plot above show the  _grade/class/cohort **attainment**_ percentiles.  Another way to visualize the historical data is to track the **attainment percentile** of this group, rather than the RIT.  To be clear: this is still the same data, derived from the same underlying RIT scores.  We're simply showing this data as an mean attainment percentile, instead of using the RIT scale.  

```{r status_trace, fig.width = 8, fig.height = 4}

status_trace_npr

```

The intuition for this plot is very straighforward - where the line is flat, it means that the class made exactly typical growth for that time period.  When the line moves up, it means that growth was _faster_ than peer grade/classes group.  If the line slopes down, it means that growth was _slower_. 

# Baseline Achievement

The `r num_students` students in this group have a baseline (`r params$baseline`) average RIT of **`r baseline_rit %>% round(1)`**.

For **grade `r params$grade` students**, that baseline puts this class at the **`r baseline_sum$cohort_status_npr %>% round(0) %>% toOrdinal::toOrdinal()`** _attainment_ percentile.  That means that this class's absolute achievement is higher than **`r baseline_sum$cohort_status_npr %>% round(0)`%** of other _classes_ in the country.

# 2016-17 Goals

Our network goal is for each class to grow at the **`r params$growth_percentile_target %>% toOrdinal::toOrdinal()`** percentile.  That's means our **growth** would be in the top **`r 100 - params$growth_percentile_target`** percent of classrooms nationally!

To reach that goal by **`r params$endpoint`**, your students will need to make **`r goal_growth %>% round(1)`** points of RIT growth on average.  That means growing from an average RIT of **`r baseline_rit %>% round(1)`** to an average RIT of **`r goal_endpoint_rit %>% round(1)`**.

If your students grew to an average RIT of **`r goal_endpoint_rit %>% round(1)`** by this Spring, they would be in the **`r goal_endpoint_cohort_status_npr %>% round(0) %>% toOrdinal::toOrdinal()`** attainment percentile.

The chart below shows how much growth is needed to hit other cohort growth benchmarks.

# More growth scenarios

```{r scens}
p_cgp_targets

```

```{r linking, eval=nys_logical, child = 'nys.Rmd'}

```

# Progress monitoring

When we test students again in the Winter, the target is for students to be **halfway** toward their Spring goal.  If the average RIT score for these students is at or above **`r goal_halfway_rit  %>% round(1)`**, that will indicate that your students are on track to reach the growth goal. 

# Student detail

The tables below shows the baseline achievement data for each of the `r num_students` in this report.

## Quartile 1 (1st percentile - 24th percentile) Students

```{r q1}

baseline_cdf <- roster_to_cdf(baseline_cdf, params$mv, 'studentfirstlast')

cdf_cols_pipe <- . %>%
  dplyr::ungroup() %>%
  dplyr::select(
    studentfirstlast, studentid, testritscore, testpercentile
  ) %>% 
  knitr::kable()

baseline_cdf %>%
  dplyr::filter(testquartile == 1)  %>%
  cdf_cols_pipe

```

## Quartile 2 (25th percentile - 49th percentile) Students

```{r q2}

baseline_cdf %>%
  dplyr::filter(testquartile == 2)  %>%
  cdf_cols_pipe

```

## Quartile 3 (50th percentile - 74th percentile) Students

```{r q3}

baseline_cdf %>%
  dplyr::filter(testquartile == 3)  %>%
  cdf_cols_pipe

```

## Quartile 4 (75th percentile - 99th percentile) Students

```{r q4}

baseline_cdf %>%
  dplyr::filter(testquartile == 4)  %>%
  cdf_cols_pipe

```
