---
output: 
  word_document:
    reference_docx: "../inst/report_templates/slim_template.docx"
params:
   mv: !r NA
   studentids: !r NA
   grade: !r NA
   growth_percentile_target: 80
   measurementscale: 'Reading'
   baseline: 'Spring 2015-2016'
   endpoint: 'Spring 2016-2017'
---

---
title: `r paste(params$measurementscale, 'MAP Goals')`
---

```{r setup, echo=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  error = FALSE
)
```

```{r}

library(gridExtra)

```

```{r}

baseline_cdf <- mapvizieR::mv_limit_cdf(
  mapvizieR_obj = params$mv,
  studentids = params$studentids,
  measurementscale = params$measurementscale
) %>%
dplyr::filter(
  termname == params$baseline
)

baseline_rit <- mean(baseline_cdf$testritscore, na.rm = TRUE) 

baseline_sum <- mapvizieR::summary.mapvizieR_cdf(baseline_cdf)

num_students <- length(params$studentids %>% unique())
valid_mask <- params$studentids %in% baseline_cdf[!is.na(baseline_cdf$testritscore), ]$studentid
num_missing <- num_students - sum(valid_mask)
missing_logical <- num_missing > 0
```

```{r}

start_season <- gsub(" .*$", "", params$baseline)
end_season <- gsub(" .*$", "", params$endpoint)

cgp_slim <- calc_cgp(
  measurementscale = params$measurementscale,
  end_grade = params$grade + 1,
  growth_window = paste0(start_season, ' to ', end_season),
  baseline_avg_rit = baseline_sum$mean_testritscore,
  calc_for = c(1, 5, 20, 50, 80, 95, 99)
)

```

```{r}

cgp_targets <- cgp_slim$targets

goal_growth <- cgp_targets[cgp_targets$cgp == params$growth_percentile_target, ]$growth_target
goal_endpoint_rit <- baseline_rit + goal_growth

goal_endpoint_cohort_status_npr <- cohort_mean_rit_to_npr(
  params$measurementscale, 
  params$grade + 1, 
  end_season,
  goal_endpoint_rit
)
```


```{r}

p_cgp_targets <- cgp_target_spread_plot(
  cgp_prep = cgp_slim
)

```

```{r}

#make plots
rit_trace_simple <- cohort_rit_trace_plot(
  mapvizieR_obj = params$mv,
  studentids = params$studentids,
  measurementscale = params$measurementscale,
  match_method = 'no matching',
  first_and_spring_only = FALSE,
  entry_grade_seasons = c(-99),
  collapse_schools = TRUE,
  retention_strategy = 'collapse',
  small_n_cutoff = -1
)

status_trace_rit <- cohort_status_trace_plot(
  mapvizieR_obj = params$mv,
  studentids = params$studentids,
  measurementscale = params$measurementscale,
  match_method = 'no matching',
  first_and_spring_only = TRUE,
  entry_grade_seasons = c(-99),
  collapse_schools = TRUE,
  retention_strategy = 'collapse',
  small_n_cutoff = -1,
  plot_labels = 'RIT'
)

status_trace_npr <- cohort_status_trace_plot(
  mapvizieR_obj = params$mv,
  studentids = params$studentids,
  measurementscale = params$measurementscale,
  match_method = 'no matching',
  first_and_spring_only = TRUE,
  entry_grade_seasons = c(-99),
  collapse_schools = TRUE,
  retention_strategy = 'collapse',
  small_n_cutoff = -1,
  plot_labels = 'NPR'
)

```


# About these students

There are `r num_students` students in this group.  **`r num_valid`** of them have a MAP score from `r params$baseline`. 

```{r include = missing_logical}

paste(
  "The", num_missing, "students with missing baseline scores are: ",
  paste(shQuote(params$studentids[!valid_mask]), collapse=", ")
)

```

# `r params$measurementscale` Prior Achievement

Here is the historical class average RIT for these students.  (This plot shows all historical data for all `r num_students` students - not only _continuously_ enrolled students.  It does not include students who have transferred out of the school and are not in the `r num_students`-student group.)

```{r,  fig.width = 8, fig.height = 4}

rit_trace_simple

```

The background reference lines on the plot above show the  _grade/class/cohort **attainment**_ percentiles.  Another way to visualize the historical data is 

```{r, fig.width = 8, fig.height = 4}

gridExtra::grid.arrange(
  status_trace_rit,
  status_trace_npr,
  ncol = 2
)

```

# Baseline Achievement

The `r num_students` students in this group have a baseline (`r params$baseline`) average RIT of **`r baseline_rit %>% round(1)`**.

For **grade `r params$grade` students**, that baseline puts this class at the **`r baseline_sum$cohort_status_npr %>% round(0) %>% toOrdinal::toOrdinal()`** _attainment_ percentile.  That means that this class's absolute achievement is higher than **`r baseline_sum$cohort_status_npr %>% round(0)`%** of other _classes_ in the country.

# 2016-17 Goals

Our network goal is for each class to grow at the **`r params$growth_percentile_target %>% toOrdinal::toOrdinal()`** percentile.  That's the top **`r 100 - params$growth_percentile_target`** percent of classrooms nationally!

To reach that goal by **`r params$endpoint`**, your students will need to make **`r goal_growth %>% round(1)`** points of RIT growth on average.  That means growing from an average RIT of **`r baseline_rit %>% round(1)`** to an average RIT of **`r goal_endpoint_rit %>% round(1)`**.

If your students grew to an average RIT of **`r goal_endpoint_rit %>% round(1)`** by this Spring, they would be in the **`r goal_endpoint_cohort_status_npr %>% round(0) %>% toOrdinal::toOrdinal()`** attainment percentile.

# Other growth benchmarks


```{r}
p_cgp_targets

```

