---
title: "NY proficiency curves"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{NY proficiency curves}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r include=FALSE, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE, cache=FALSE}
# This vignette generates data files and shouldn't be executed during pkgdown build
knitr::opts_chunk$set(eval = FALSE)
library(mapvizieR)
```

NWEA publishes probability estimates from 0-1 that a student will pass the NY State assessment given a particular RIT/Grade/Season.  The [pdf](https://www.nwea.org/content/uploads/2016/03/New_York_-Linking_Study_MAR2016.pdf) report publishes these estimates in 5 percentile bands.  Clearly, there's an underlying logistic regression model that expresses `pass likelihood ~ MAP percentile`.  

## Data file with predicted pass

```{r}

ny_read_spr_g3_l1 <- data.frame(
  ny_subj = 'Reading',
  ny_grade = 3,
  ny_season = 'Spring',
  ny_rit = c(100:195),
  perf_level = 'Level 1',
  proficient = FALSE,
  stringsAsFactors = FALSE
)
ny_read_spr_g3_l2 <- data.frame(
  ny_subj = 'Reading',
  ny_grade = 3,
  ny_season = 'Spring',
  ny_rit = c(196:207),
  perf_level = 'Level 2',
  proficient = FALSE,
  stringsAsFactors = FALSE
)
ny_read_spr_g3_l3 <- data.frame(
  ny_subj = 'Reading',
  ny_grade = 3,
  ny_season = 'Spring',
  ny_rit = c(208:221),
  perf_level = 'Level 3',
  proficient = TRUE,
  stringsAsFactors = FALSE
)
ny_read_spr_g3_l4 <- data.frame(
  ny_subj = 'Reading',
  ny_grade = 3,
  ny_season = 'Spring',
  ny_rit = c(222:350),
  perf_level = 'Level 4',
  proficient = TRUE,
  stringsAsFactors = FALSE
)

ny_read_spr_g4_l1 <- data.frame(
  ny_subj = 'Reading',
  ny_grade = 4,
  ny_season = 'Spring',
  ny_rit = c(100:202),
  perf_level = 'Level 1',
  proficient = FALSE,
  stringsAsFactors = FALSE
)
ny_read_spr_g4_l2 <- data.frame(
  ny_subj = 'Reading',
  ny_grade = 4,
  ny_season = 'Spring',
  ny_rit = c(203:215),
  perf_level = 'Level 2',
  proficient = FALSE,
  stringsAsFactors = FALSE
)
ny_read_spr_g4_l3 <- data.frame(
  ny_subj = 'Reading',
  ny_grade = 4,
  ny_season = 'Spring',
  ny_rit = c(216:223),
  perf_level = 'Level 3',
  proficient = TRUE,
  stringsAsFactors = FALSE
)
ny_read_spr_g4_l4 <- data.frame(
  ny_subj = 'Reading',
  ny_grade = 4,
  ny_season = 'Spring',
  ny_rit = c(224:350),
  perf_level = 'Level 4',
  proficient = TRUE,
  stringsAsFactors = FALSE
)

ny_read_spr_g5_l1 <- data.frame(
  ny_subj = 'Reading',
  ny_grade = 5,
  ny_season = 'Spring',
  ny_rit = c(100:209),
  perf_level = 'Level 1',
  proficient = FALSE,
  stringsAsFactors = FALSE
)
ny_read_spr_g5_l2 <- data.frame(
  ny_subj = 'Reading',
  ny_grade = 5,
  ny_season = 'Spring',
  ny_rit = c(210:221),
  perf_level = 'Level 2',
  proficient = FALSE,
  stringsAsFactors = FALSE
)
ny_read_spr_g5_l3 <- data.frame(
  ny_subj = 'Reading',
  ny_grade = 5,
  ny_season = 'Spring',
  ny_rit = c(222:230),
  perf_level = 'Level 3',
  proficient = TRUE,
  stringsAsFactors = FALSE
)
ny_read_spr_g5_l4 <- data.frame(
  ny_subj = 'Reading',
  ny_grade = 5,
  ny_season = 'Spring',
  ny_rit = c(231:350),
  perf_level = 'Level 4',
  proficient = TRUE,
  stringsAsFactors = FALSE
)

ny_read_spr_g6_l1 <- data.frame(
  ny_subj = 'Reading',
  ny_grade = 6,
  ny_season = 'Spring',
  ny_rit = c(100:210),
  perf_level = 'Level 1',
  proficient = FALSE,
  stringsAsFactors = FALSE
)
ny_read_spr_g6_l2 <- data.frame(
  ny_subj = 'Reading',
  ny_grade = 6,
  ny_season = 'Spring',
  ny_rit = c(211:224),
  perf_level = 'Level 2',
  proficient = FALSE,
  stringsAsFactors = FALSE
)
ny_read_spr_g6_l3 <- data.frame(
  ny_subj = 'Reading',
  ny_grade = 6,
  ny_season = 'Spring',
  ny_rit = c(225:231),
  perf_level = 'Level 3',
  proficient = TRUE,
  stringsAsFactors = FALSE
)
ny_read_spr_g6_l4 <- data.frame(
  ny_subj = 'Reading',
  ny_grade = 6,
  ny_season = 'Spring',
  ny_rit = c(232:350),
  perf_level = 'Level 4',
  proficient = TRUE,
  stringsAsFactors = FALSE
)

ny_read_spr_g7_l1 <- data.frame(
  ny_subj = 'Reading',
  ny_grade = 7,
  ny_season = 'Spring',
  ny_rit = c(100:215),
  perf_level = 'Level 1',
  proficient = FALSE,
  stringsAsFactors = FALSE
)
ny_read_spr_g7_l2 <- data.frame(
  ny_subj = 'Reading',
  ny_grade = 7,
  ny_season = 'Spring',
  ny_rit = c(216:227),
  perf_level = 'Level 2',
  proficient = FALSE,
  stringsAsFactors = FALSE
)
ny_read_spr_g7_l3 <- data.frame(
  ny_subj = 'Reading',
  ny_grade = 7,
  ny_season = 'Spring',
  ny_rit = c(228:238),
  perf_level = 'Level 3',
  proficient = TRUE,
  stringsAsFactors = FALSE
)
ny_read_spr_g7_l4 <- data.frame(
  ny_subj = 'Reading',
  ny_grade = 7,
  ny_season = 'Spring',
  ny_rit = c(239:350),
  perf_level = 'Level 4',
  proficient = TRUE,
  stringsAsFactors = FALSE
)

ny_read_spr_g8_l1 <- data.frame(
  ny_subj = 'Reading',
  ny_grade = 8,
  ny_season = 'Spring',
  ny_rit = c(100:218),
  perf_level = 'Level 1',
  proficient = FALSE,
  stringsAsFactors = FALSE
)
ny_read_spr_g8_l2 <- data.frame(
  ny_subj = 'Reading',
  ny_grade = 8,
  ny_season = 'Spring',
  ny_rit = c(219:230),
  perf_level = 'Level 2',
  proficient = FALSE,
  stringsAsFactors = FALSE
)
ny_read_spr_g8_l3 <- data.frame(
  ny_subj = 'Reading',
  ny_grade = 8,
  ny_season = 'Spring',
  ny_rit = c(231:240),
  perf_level = 'Level 3',
  proficient = TRUE,
  stringsAsFactors = FALSE
)
ny_read_spr_g8_l4 <- data.frame(
  ny_subj = 'Reading',
  ny_grade = 8,
  ny_season = 'Spring',
  ny_rit = c(241:350),
  perf_level = 'Level 4',
  proficient = TRUE,
  stringsAsFactors = FALSE
)

ny_math_spr_g3_l1 <- data.frame(
  ny_subj = 'Mathematics',
  ny_grade = 3,
  ny_season = 'Spring',
  ny_rit = c(100:195),
  perf_level = 'Level 1',
  proficient = FALSE,
  stringsAsFactors = FALSE
)  
ny_math_spr_g3_l2 <- data.frame(
  ny_subj = 'Mathematics',
  ny_grade = 3,
  ny_season = 'Spring',
  ny_rit = c(196:205),
  perf_level = 'Level 2',
  proficient = FALSE,
  stringsAsFactors = FALSE
)
ny_math_spr_g3_l3 <- data.frame(
  ny_subj = 'Mathematics',
  ny_grade = 3,
  ny_season = 'Spring',
  ny_rit = c(206:214),
  perf_level = 'Level 3',
  proficient = TRUE,
  stringsAsFactors = FALSE
)
ny_math_spr_g3_l4 <- data.frame(
  ny_subj = 'Mathematics',
  ny_grade = 3,
  ny_season = 'Spring',
  ny_rit = c(215:350),
  perf_level = 'Level 4',
  proficient = TRUE,
  stringsAsFactors = FALSE
)

ny_math_spr_g4_l1 <- data.frame(
  ny_subj = 'Mathematics',
  ny_grade = 4,
  ny_season = 'Spring',
  ny_rit = c(100:205),
  perf_level = 'Level 1',
  proficient = FALSE,
  stringsAsFactors = FALSE
)
ny_math_spr_g4_l2 <- data.frame(
  ny_subj = 'Mathematics',
  ny_grade = 4,
  ny_season = 'Spring',
  ny_rit = c(206:219),
  perf_level = 'Level 2',
  proficient = FALSE,
  stringsAsFactors = FALSE
)
ny_math_spr_g4_l3 <- data.frame(
  ny_subj = 'Mathematics',
  ny_grade = 4,
  ny_season = 'Spring',
  ny_rit = c(220:233),
  perf_level = 'Level 3',
  proficient = TRUE,
  stringsAsFactors = FALSE
)
ny_math_spr_g4_l4 <- data.frame(
  ny_subj = 'Mathematics',
  ny_grade = 4,
  ny_season = 'Spring',
  ny_rit = c(234:350),
  perf_level = 'Level 4',
  proficient = TRUE,
  stringsAsFactors = FALSE
)

ny_math_spr_g5_l1 <- data.frame(
  ny_subj = 'Mathematics',
  ny_grade = 5,
  ny_season = 'Spring',
  ny_rit = c(100:218),
  perf_level = 'Level 1',
  proficient = FALSE,
  stringsAsFactors = FALSE
)
ny_math_spr_g5_l2 <- data.frame(
  ny_subj = 'Mathematics',
  ny_grade = 5,
  ny_season = 'Spring',
  ny_rit = c(219:231),
  perf_level = 'Level 2',
  proficient = FALSE,
  stringsAsFactors = FALSE
)
ny_math_spr_g5_l3 <- data.frame(
  ny_subj = 'Mathematics',
  ny_grade = 5,
  ny_season = 'Spring',
  ny_rit = c(232:246),
  perf_level = 'Level 3',
  proficient = TRUE,
  stringsAsFactors = FALSE
)
ny_math_spr_g5_l4 <- data.frame(
  ny_subj = 'Mathematics',
  ny_grade = 5,
  ny_season = 'Spring',
  ny_rit = c(247:350),
  perf_level = 'Level 4',
  proficient = TRUE,
  stringsAsFactors = FALSE
)

ny_math_spr_g6_l1 <- data.frame(
  ny_subj = 'Mathematics',
  ny_grade = 6,
  ny_season = 'Spring',
  ny_rit = c(100:216),
  perf_level = 'Level 1',
  proficient = FALSE,
  stringsAsFactors = FALSE
)
ny_math_spr_g6_l2 <- data.frame(
  ny_subj = 'Mathematics',
  ny_grade = 6,
  ny_season = 'Spring',
  ny_rit = c(217:231),
  perf_level = 'Level 2',
  proficient = FALSE,
  stringsAsFactors = FALSE
)
ny_math_spr_g6_l3 <- data.frame(
  ny_subj = 'Mathematics',
  ny_grade = 6,
  ny_season = 'Spring',
  ny_rit = c(232:241),
  perf_level = 'Level 3',
  proficient = TRUE,
  stringsAsFactors = FALSE
)
ny_math_spr_g6_l4 <- data.frame(
  ny_subj = 'Mathematics',
  ny_grade = 6,
  ny_season = 'Spring',
  ny_rit = c(242:350),
  perf_level = 'Level 4',
  proficient = TRUE,
  stringsAsFactors = FALSE
)

ny_math_spr_g7_l1 <- data.frame(
  ny_subj = 'Mathematics',
  ny_grade = 7,
  ny_season = 'Spring',
  ny_rit = c(100:226),
  perf_level = 'Level 1',
  proficient = FALSE,
  stringsAsFactors = FALSE
)
ny_math_spr_g7_l2 <- data.frame(
  ny_subj = 'Mathematics',
  ny_grade = 7,
  ny_season = 'Spring',
  ny_rit = c(227:240),
  perf_level = 'Level 2',
  proficient = FALSE,
  stringsAsFactors = FALSE
)
ny_math_spr_g7_l3 <- data.frame(
  ny_subj = 'Mathematics',
  ny_grade = 7,
  ny_season = 'Spring',
  ny_rit = c(241:254),
  perf_level = 'Level 3',
  proficient = TRUE,
  stringsAsFactors = FALSE
)
ny_math_spr_g7_l4 <- data.frame(
  ny_subj = 'Mathematics',
  ny_grade = 7,
  ny_season = 'Spring',
  ny_rit = c(255:350),
  perf_level = 'Level 4',
  proficient = TRUE,
  stringsAsFactors = FALSE
)

ny_math_spr_g8_l1 <- data.frame(
  ny_subj = 'Mathematics',
  ny_grade = 8,
  ny_season = 'Spring',
  ny_rit = c(100:226),
  perf_level = 'Level 1',
  proficient = FALSE,
  stringsAsFactors = FALSE
)
ny_math_spr_g8_l2 <- data.frame(
  ny_subj = 'Mathematics',
  ny_grade = 8,
  ny_season = 'Spring',
  ny_rit = c(227:245),
  perf_level = 'Level 2',
  proficient = FALSE,
  stringsAsFactors = FALSE
)
ny_math_spr_g8_l3 <- data.frame(
  ny_subj = 'Mathematics',
  ny_grade = 8,
  ny_season = 'Spring',
  ny_rit = c(246:259),
  perf_level = 'Level 3',
  proficient = TRUE,
  stringsAsFactors = FALSE
)
ny_math_spr_g8_l4 <- data.frame(
  ny_subj = 'Mathematics',
  ny_grade = 8,
  ny_season = 'Spring',
  ny_rit = c(260:350),
  perf_level = 'Level 4',
  proficient = TRUE,
  stringsAsFactors = FALSE
)

ny_read_win_g3_l1 <- data.frame(
  ny_subj = 'Reading',
  ny_grade = 3,
  ny_season = 'Winter',
  ny_rit = c(100:192),
  perf_level = 'Level 1',
  proficient = FALSE,
  stringsAsFactors = FALSE
)
ny_read_win_g3_l2 <- data.frame(
  ny_subj = 'Reading',
  ny_grade = 3,
  ny_season = 'Winter',
  ny_rit = c(193:205),
  perf_level = 'Level 2',
  proficient = FALSE,
  stringsAsFactors = FALSE
)
ny_read_win_g3_l3 <- data.frame(
  ny_subj = 'Reading',
  ny_grade = 3,
  ny_season = 'Winter',
  ny_rit = c(206:220),
  perf_level = 'Level 3',
  proficient = TRUE,
  stringsAsFactors = FALSE
)
ny_read_win_g3_l4 <- data.frame(
  ny_subj = 'Reading',
  ny_grade = 3,
  ny_season = 'Winter',
  ny_rit = c(221:350),
  perf_level = 'Level 4',
  proficient = TRUE,
  stringsAsFactors = FALSE
)

ny_read_win_g4_l1 <- data.frame(
  ny_subj = 'Reading',
  ny_grade = 4,
  ny_season = 'Winter',
  ny_rit = c(100:199),
  perf_level = 'Level 1',
  proficient = FALSE,
  stringsAsFactors = FALSE
)
ny_read_win_g4_l2 <- data.frame(
  ny_subj = 'Reading',
  ny_grade = 4,
  ny_season = 'Winter',
  ny_rit = c(200:213),
  perf_level = 'Level 2',
  proficient = FALSE,
  stringsAsFactors = FALSE
)
ny_read_win_g4_l3 <- data.frame(
  ny_subj = 'Reading',
  ny_grade = 4,
  ny_season = 'Winter',
  ny_rit = c(214:222),
  perf_level = 'Level 3',
  proficient = TRUE,
  stringsAsFactors = FALSE
)
ny_read_win_g4_l4 <- data.frame(
  ny_subj = 'Reading',
  ny_grade = 4,
  ny_season = 'Winter',
  ny_rit = c(223:350),
  perf_level = 'Level 4',
  proficient = TRUE,
  stringsAsFactors = FALSE
)

ny_read_win_g5_l1 <- data.frame(
  ny_subj = 'Reading',
  ny_grade = 5,
  ny_season = 'Winter',
  ny_rit = c(100:207),
  perf_level = 'Level 1',
  proficient = FALSE,
  stringsAsFactors = FALSE
)
ny_read_win_g5_l2 <- data.frame(
  ny_subj = 'Reading',
  ny_grade = 5,
  ny_season = 'Winter',
  ny_rit = c(208:220),
  perf_level = 'Level 2',
  proficient = FALSE,
  stringsAsFactors = FALSE
)
ny_read_win_g5_l3 <- data.frame(
  ny_subj = 'Reading',
  ny_grade = 5,
  ny_season = 'Winter',
  ny_rit = c(221:229),
  perf_level = 'Level 3',
  proficient = TRUE,
  stringsAsFactors = FALSE
)
ny_read_win_g5_l4 <- data.frame(
  ny_subj = 'Reading',
  ny_grade = 5,
  ny_season = 'Winter',
  ny_rit = c(230:350),
  perf_level = 'Level 4',
  proficient = TRUE,
  stringsAsFactors = FALSE
)

ny_read_win_g6_l1 <- data.frame(
  ny_subj = 'Reading',
  ny_grade = 6,
  ny_season = 'Winter',
  ny_rit = c(100:208),
  perf_level = 'Level 1',
  proficient = FALSE,
  stringsAsFactors = FALSE
)
ny_read_win_g6_l2 <- data.frame(
  ny_subj = 'Reading',
  ny_grade = 6,
  ny_season = 'Winter',
  ny_rit = c(209:223),
  perf_level = 'Level 2',
  proficient = FALSE,
  stringsAsFactors = FALSE
)
ny_read_win_g6_l3 <- data.frame(
  ny_subj = 'Reading',
  ny_grade = 6,
  ny_season = 'Winter',
  ny_rit = c(224:230),
  perf_level = 'Level 3',
  proficient = TRUE,
  stringsAsFactors = FALSE
)
ny_read_win_g6_l4 <- data.frame(
  ny_subj = 'Reading',
  ny_grade = 6,
  ny_season = 'Winter',
  ny_rit = c(231:350),
  perf_level = 'Level 4',
  proficient = TRUE,
  stringsAsFactors = FALSE
)

ny_read_win_g7_l1 <- data.frame(
  ny_subj = 'Reading',
  ny_grade = 7,
  ny_season = 'Winter',
  ny_rit = c(100:214),
  perf_level = 'Level 1',
  proficient = FALSE,
  stringsAsFactors = FALSE
)
ny_read_win_g7_l2 <- data.frame(
  ny_subj = 'Reading',
  ny_grade = 7,
  ny_season = 'Winter',
  ny_rit = c(215:226),
  perf_level = 'Level 2',
  proficient = FALSE,
  stringsAsFactors = FALSE
)
ny_read_win_g7_l3 <- data.frame(
  ny_subj = 'Reading',
  ny_grade = 7,
  ny_season = 'Winter',
  ny_rit = c(227:237),
  perf_level = 'Level 3',
  proficient = TRUE,
  stringsAsFactors = FALSE
)
ny_read_win_g7_l4 <- data.frame(
  ny_subj = 'Reading',
  ny_grade = 7,
  ny_season = 'Winter',
  ny_rit = c(238:350),
  perf_level = 'Level 4',
  proficient = TRUE,
  stringsAsFactors = FALSE
)

ny_read_win_g8_l1 <- data.frame(
  ny_subj = 'Reading',
  ny_grade = 8,
  ny_season = 'Winter',
  ny_rit = c(100:217),
  perf_level = 'Level 1',
  proficient = FALSE,
  stringsAsFactors = FALSE
)
ny_read_win_g8_l2 <- data.frame(
  ny_subj = 'Reading',
  ny_grade = 8,
  ny_season = 'Winter',
  ny_rit = c(218:229),
  perf_level = 'Level 2',
  proficient = FALSE,
  stringsAsFactors = FALSE
)
ny_read_win_g8_l3 <- data.frame(
  ny_subj = 'Reading',
  ny_grade = 8,
  ny_season = 'Winter',
  ny_rit = c(230:239),
  perf_level = 'Level 3',
  proficient = TRUE,
  stringsAsFactors = FALSE
)
ny_read_win_g8_l4 <- data.frame(
  ny_subj = 'Reading',
  ny_grade = 8,
  ny_season = 'Winter',
  ny_rit = c(240:350),
  perf_level = 'Level 4',
  proficient = TRUE,
  stringsAsFactors = FALSE
)

ny_math_win_g3_l1 <- data.frame(
  ny_subj = 'Mathematics',
  ny_grade = 3,
  ny_season = 'Winter',
  ny_rit = c(100:190),
  perf_level = 'Level 1',
  proficient = FALSE,
  stringsAsFactors = FALSE
)  
ny_math_win_g3_l2 <- data.frame(
  ny_subj = 'Mathematics',
  ny_grade = 3,
  ny_season = 'Winter',
  ny_rit = c(191:200),
  perf_level = 'Level 2',
  proficient = FALSE,
  stringsAsFactors = FALSE
)
ny_math_win_g3_l3 <- data.frame(
  ny_subj = 'Mathematics',
  ny_grade = 3,
  ny_season = 'Winter',
  ny_rit = c(201:209),
  perf_level = 'Level 3',
  proficient = TRUE,
  stringsAsFactors = FALSE
)
ny_math_win_g3_l4 <- data.frame(
  ny_subj = 'Mathematics',
  ny_grade = 3,
  ny_season = 'Winter',
  ny_rit = c(210:350),
  perf_level = 'Level 4',
  proficient = TRUE,
  stringsAsFactors = FALSE
)

ny_math_win_g4_l1 <- data.frame(
  ny_subj = 'Mathematics',
  ny_grade = 4,
  ny_season = 'Winter',
  ny_rit = c(100:200),
  perf_level = 'Level 1',
  proficient = FALSE,
  stringsAsFactors = FALSE
)
ny_math_win_g4_l2 <- data.frame(
  ny_subj = 'Mathematics',
  ny_grade = 4,
  ny_season = 'Winter',
  ny_rit = c(201:214),
  perf_level = 'Level 2',
  proficient = FALSE,
  stringsAsFactors = FALSE
)
ny_math_win_g4_l3 <- data.frame(
  ny_subj = 'Mathematics',
  ny_grade = 4,
  ny_season = 'Winter',
  ny_rit = c(215:228),
  perf_level = 'Level 3',
  proficient = TRUE,
  stringsAsFactors = FALSE
)
ny_math_win_g4_l4 <- data.frame(
  ny_subj = 'Mathematics',
  ny_grade = 4,
  ny_season = 'Winter',
  ny_rit = c(229:350),
  perf_level = 'Level 4',
  proficient = TRUE,
  stringsAsFactors = FALSE
)

ny_math_win_g5_l1 <- data.frame(
  ny_subj = 'Mathematics',
  ny_grade = 5,
  ny_season = 'Winter',
  ny_rit = c(100:214),
  perf_level = 'Level 1',
  proficient = FALSE,
  stringsAsFactors = FALSE
)
ny_math_win_g5_l2 <- data.frame(
  ny_subj = 'Mathematics',
  ny_grade = 5,
  ny_season = 'Winter',
  ny_rit = c(215:227),
  perf_level = 'Level 2',
  proficient = FALSE,
  stringsAsFactors = FALSE
)
ny_math_win_g5_l3 <- data.frame(
  ny_subj = 'Mathematics',
  ny_grade = 5,
  ny_season = 'Winter',
  ny_rit = c(228:242),
  perf_level = 'Level 3',
  proficient = TRUE,
  stringsAsFactors = FALSE
)
ny_math_win_g5_l4 <- data.frame(
  ny_subj = 'Mathematics',
  ny_grade = 5,
  ny_season = 'Winter',
  ny_rit = c(243:350),
  perf_level = 'Level 4',
  proficient = TRUE,
  stringsAsFactors = FALSE
)

ny_math_win_g6_l1 <- data.frame(
  ny_subj = 'Mathematics',
  ny_grade = 6,
  ny_season = 'Winter',
  ny_rit = c(100:213),
  perf_level = 'Level 1',
  proficient = FALSE,
  stringsAsFactors = FALSE
)
ny_math_win_g6_l2 <- data.frame(
  ny_subj = 'Mathematics',
  ny_grade = 6,
  ny_season = 'Winter',
  ny_rit = c(214:228),
  perf_level = 'Level 2',
  proficient = FALSE,
  stringsAsFactors = FALSE
)
ny_math_win_g6_l3 <- data.frame(
  ny_subj = 'Mathematics',
  ny_grade = 6,
  ny_season = 'Winter',
  ny_rit = c(229:238),
  perf_level = 'Level 3',
  proficient = TRUE,
  stringsAsFactors = FALSE
)
ny_math_win_g6_l4 <- data.frame(
  ny_subj = 'Mathematics',
  ny_grade = 6,
  ny_season = 'Winter',
  ny_rit = c(239:350),
  perf_level = 'Level 4',
  proficient = TRUE,
  stringsAsFactors = FALSE
)

ny_math_win_g7_l1 <- data.frame(
  ny_subj = 'Mathematics',
  ny_grade = 7,
  ny_season = 'Winter',
  ny_rit = c(100:224),
  perf_level = 'Level 1',
  proficient = FALSE,
  stringsAsFactors = FALSE
)
ny_math_win_g7_l2 <- data.frame(
  ny_subj = 'Mathematics',
  ny_grade = 7,
  ny_season = 'Winter',
  ny_rit = c(225:238),
  perf_level = 'Level 2',
  proficient = FALSE,
  stringsAsFactors = FALSE
)
ny_math_win_g7_l3 <- data.frame(
  ny_subj = 'Mathematics',
  ny_grade = 7,
  ny_season = 'Winter',
  ny_rit = c(239:252),
  perf_level = 'Level 3',
  proficient = TRUE,
  stringsAsFactors = FALSE
)
ny_math_win_g7_l4 <- data.frame(
  ny_subj = 'Mathematics',
  ny_grade = 7,
  ny_season = 'Winter',
  ny_rit = c(253:350),
  perf_level = 'Level 4',
  proficient = TRUE,
  stringsAsFactors = FALSE
)

ny_math_win_g8_l1 <- data.frame(
  ny_subj = 'Mathematics',
  ny_grade = 8,
  ny_season = 'Winter',
  ny_rit = c(100:224),
  perf_level = 'Level 1',
  proficient = FALSE,
  stringsAsFactors = FALSE
)
ny_math_win_g8_l2 <- data.frame(
  ny_subj = 'Mathematics',
  ny_grade = 8,
  ny_season = 'Winter',
  ny_rit = c(225:243),
  perf_level = 'Level 2',
  proficient = FALSE,
  stringsAsFactors = FALSE
)
ny_math_win_g8_l3 <- data.frame(
  ny_subj = 'Mathematics',
  ny_grade = 8,
  ny_season = 'Winter',
  ny_rit = c(244:257),
  perf_level = 'Level 3',
  proficient = TRUE,
  stringsAsFactors = FALSE
)
ny_math_win_g8_l4 <- data.frame(
  ny_subj = 'Mathematics',
  ny_grade = 8,
  ny_season = 'Winter',
  ny_rit = c(258:350),
  perf_level = 'Level 4',
  proficient = TRUE,
  stringsAsFactors = FALSE
)  

ny_predicted_proficiency <- dplyr::bind_rows(
  ny_read_spr_g3_l1, ny_read_spr_g3_l2, ny_read_spr_g3_l3, ny_read_spr_g3_l4,
  ny_read_spr_g4_l1, ny_read_spr_g4_l2, ny_read_spr_g4_l3, ny_read_spr_g4_l4,
  ny_read_spr_g5_l1, ny_read_spr_g5_l2, ny_read_spr_g5_l3, ny_read_spr_g5_l4,
  ny_read_spr_g6_l1, ny_read_spr_g6_l2, ny_read_spr_g6_l3, ny_read_spr_g6_l4,
  ny_read_spr_g7_l1, ny_read_spr_g7_l2, ny_read_spr_g7_l3, ny_read_spr_g7_l4,
  ny_read_spr_g8_l1, ny_read_spr_g8_l2, ny_read_spr_g8_l3, ny_read_spr_g8_l4,
  
  ny_math_spr_g3_l1, ny_math_spr_g3_l2, ny_math_spr_g3_l3, ny_math_spr_g3_l4,
  ny_math_spr_g4_l1, ny_math_spr_g4_l2, ny_math_spr_g4_l3, ny_math_spr_g4_l4,
  ny_math_spr_g5_l1, ny_math_spr_g5_l2, ny_math_spr_g5_l3, ny_math_spr_g5_l4,
  ny_math_spr_g6_l1, ny_math_spr_g6_l2, ny_math_spr_g6_l3, ny_math_spr_g6_l4,
  ny_math_spr_g7_l1, ny_math_spr_g7_l2, ny_math_spr_g7_l3, ny_math_spr_g7_l4,
  ny_math_spr_g8_l1, ny_math_spr_g8_l2, ny_math_spr_g8_l3, ny_math_spr_g8_l4,
  
  ny_read_win_g3_l1, ny_read_win_g3_l2, ny_read_win_g3_l3, ny_read_win_g3_l4,
  ny_read_win_g4_l1, ny_read_win_g4_l2, ny_read_win_g4_l3, ny_read_win_g4_l4,
  ny_read_win_g5_l1, ny_read_win_g5_l2, ny_read_win_g5_l3, ny_read_win_g5_l4,
  ny_read_win_g6_l1, ny_read_win_g6_l2, ny_read_win_g6_l3, ny_read_win_g6_l4,
  ny_read_win_g7_l1, ny_read_win_g7_l2, ny_read_win_g7_l3, ny_read_win_g7_l4,
  ny_read_win_g8_l1, ny_read_win_g8_l2, ny_read_win_g8_l3, ny_read_win_g8_l4,
  
  ny_math_win_g3_l1, ny_math_win_g3_l2, ny_math_win_g3_l3, ny_math_win_g3_l4,
  ny_math_win_g4_l1, ny_math_win_g4_l2, ny_math_win_g4_l3, ny_math_win_g4_l4,
  ny_math_win_g5_l1, ny_math_win_g5_l2, ny_math_win_g5_l3, ny_math_win_g5_l4,
  ny_math_win_g6_l1, ny_math_win_g6_l2, ny_math_win_g6_l3, ny_math_win_g6_l4,
  ny_math_win_g7_l1, ny_math_win_g7_l2, ny_math_win_g7_l3, ny_math_win_g7_l4,
  ny_math_win_g8_l1, ny_math_win_g8_l2, ny_math_win_g8_l3, ny_math_win_g8_l4    
)

save(ny_predicted_proficiency, file = file.path('data', 'ny_predicted_proficiency.rda'))


```


## Read in the raw data
```{r}

ny <- read.csv(
  file = file.path('data-raw', 'ny_linking_curves_tidy.csv'),
  stringsAsFactors = FALSE
)

peek(ny)

unq_models <- ny[, c('Grade', 'Measurementscale', 'Season')] %>% unique()

```

## Iterate and fit a logistic regression to each data set
```{r}

all_preds <- list()

for (i in seq_len(nrow(unq_models))) {
  
  ids <- unq_models[i, ]
  
  this_raw <- ny[ny$Grade == ids$Grade & 
       ny$Measurementscale == ids$Measurementscale &
       ny$Season == ids$Season, ]
  
  fit <- glm(Probability ~ Percentile, family = binomial, data = this_raw)
  new_pred <- predict(
    fit, 
    newdata = data.frame(Percentile = seq(1, 99, 1)), 
    type = 'response',
    interval = 'prediction'
  ) %>% round(4)
  
  pred_df <- data.frame(
    grade = ids$Grade,
    measurementscale = ids$Measurementscale,
    fallwinterspring = ids$Season,
    percentile = seq(1, 99, 1),
    pass_probability = new_pred,
    stringsAsFactors = FALSE
  )
  
  all_preds[[i]] <- pred_df
}

ny_predicted_pass <- dplyr::rbind_all(all_preds)
peek(ny_predicted_pass)

```

Save the data to the package

```{r}

save(ny_predicted_pass, file = file.path('data', 'ny_predicted_pass.rda'))

```