---
title: "NY proficiency curves"
output: html_document
---


```{r include=FALSE, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE, cache=FALSE}

library(mapvizieR)

```
NWEA publishes probability estimates from 0-1 that a student will pass the NY State assessment given a particular RIT/Grade/Season.  The [pdf](https://www.nwea.org/content/uploads/2016/03/New_York_-Linking_Study_MAR2016.pdf) report publishes these estimates in 5 percentile bands.  Clearly, there's an underlying logistic regression model that expresses `pass likelihood ~ MAP percentile`.  

## Read in the raw data
```{r}

ny <- read.csv(
  file = file.path('data-raw', 'ny_linking_curves_tidy.csv'),
  stringsAsFactors = FALSE
)

peek(ny)

unq_models <- ny[, c('Grade', 'Measurementscale', 'Season')] %>% unique()

```

## Iterate and fit a logistic regression to each data set
```{r}

all_preds <- list()

for (i in 1:nrow(unq_models)) {
  
  ids <- unq_models[i, ]
  
  this_raw <- ny[ny$Grade == ids$Grade & 
       ny$Measurementscale == ids$Measurementscale &
       ny$Season == ids$Season, ]
  
  fit <- glm(Probability ~ Percentile, family = binomial, data = this_raw)
  new_pred <- predict(
    fit, 
    newdata = data.frame(Percentile = seq(1, 99, 1)), 
    type = 'response',
    interval = 'prediction'
  ) %>% round(4)
  
  pred_df <- data.frame(
    grade = ids$Grade,
    measurementscale = ids$Measurementscale,
    fallwinterspring = ids$Season,
    percentile = seq(1, 99, 1),
    pass_probability = new_pred,
    stringsAsFactors = FALSE
  )
  
  all_preds[[i]] <- pred_df
}

ny_linking <- dplyr::rbind_all(all_preds)
peek(ny_linking)

```

Save the data to the package

```{r}

save(ny_linking, file = file.path('data', 'ny_linking.rda'))

```